---
title: "Iteration and Listcols"
author: "Maya Krishnamoorthy"
date: "2024-10-29"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

set.seed(1)
```

## Lists

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)

l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```


Make a list that's hopefully more useful.

```{r}
list_norm = 
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 40, 10)
  )

list_norm[["b"]]
```

Let's reuse the function we wrote last time.

```{r}
mean_and_sd = function(x) {
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  output_df =
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(output_df)
}
```

Use the function to take mean and sd of all samples.

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])

```

## Use a for loop

Create output list, and run a for loop.

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}

output
```

## Do the same thing
but with `map` instead

```{r}
map(list_norm, mean_and_sd)

output =
  map(list_norm, mean_and_sd) |> 
  bind_rows()

output = map_dbl(list_norm, IQR)

```

## LIST COLUMNS!

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )

listcol_df

listcol_df |> 
  filter(name %in% c("a", "b"))

listcol_df |> 
  select(-samp)
```

```{r}
listcol_df[["samp"]][["a"]]
```

Compute mean and sd

```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])
mean_and_sd(listcol_df[["samp"]][["b"]])

map(listcol_df[["samp"]], mean_and_sd)
```

ADD A LIST COLUMN!

```{r}
listcol_df |> 
  mutate(
    output = map(samp, mean_and_sd),
    iqr = map_dbl(samp, IQR)
  )

listcol_df |> 
  mutate(
    output = map_dfr(samp, mean_and_sd),
    iqr = map_dbl(samp, IQR)
  ) |> 
  select(-samp) |> 
  unnest(output)
```


### NSDUH

This is a version of our function last time.

```{r}
nsduh_table = function(html, table_num) {
  out_table = 
    html |> 
    html_table() |> 
    nth(table_num) |>
    slice(-1) |> 
    select(-contains("P Value"))
  
  return(out_table)
  
}

```


We need to import the html, and then extract the correct tables.

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```

```{r}
nsduh_table(html = nsduh_html, table_num = 1)
nsduh_table(html = nsduh_html, table_num = 4)
nsduh_table(html = nsduh_html, table_num = 5)
```

```{r}
nsduh_df = 
  tibble(
    drug = c("marj", "cocaine", "heroin"),
    table_n = c(1, 4, 5)
  ) |> 
  mutate(table = map(table_n, nsduh_table, html = nsduh_html)) |> 
  unnest(table)

nsduh_df |> 
  filter(State == "New York")
```



```{r}

```

